Efficient Coalition Formation for Web Services

### 2013-03-01 papers/coalition/coalition.tex
Changes

The second condition is $feasibility$, according to equation below the payoff for each agent cannot be more than coalitions total gain. A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.

When dealing with cooperative games, two issues need to get addressed: 1. What coalition to form? 2. How to reward each each member when a task is completed?

@@

{\bf Definition 1 (Core)}

>>>>

The second condition is $feasibility$, according to equation below the payoff for each agent cannot be more than coalitions total gain. A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of characteristic function works in $transferable utility$ (TU) settings, where utility (payoff) is transfarable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.

When dealing with cooperative games, two issues need to get addressed: 1. What coalition to form (Canonical games)? 2. How to reward each each member when a task is completed (Coalition-formation games)?

@@

{\bf Definition 2 (Core)} A payoff vector x denoted by C(N,v) is in the core of a coalitional game (N, v) if and only if
\begin{equation}\label{eq:core}
\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
\end{equation}
The core if is not empty is basicly a payoff vector (x) where no where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
